Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-04-01 Article/article.tex
minor

\end{itemize}
\todo[inline]{SKumar: equivalent tikz figure}
\begin{tabular}{|l|l|l|}
\hline
Task & Comm Time & Comp Time\\ \hline
A & 3 & 2\\ \hline
B & 1 & 3\\ \hline
C & 4 & 4\\ \hline
D & 2 & 1\\ \hline
\end{tabular}
	\begin{figure}[htb]
	\centering
%% 	\subfloat[Optimal schedule]{
		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.5, every node/.style={scale=0.5}]
		\tikzstyle{legend}=[below=0.25, anchor=mid] 	
		\node(t1) at (0,0) {};

	    \node[above right=0.8cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=13cm, draw=white, fill=white](IMC) {$Infinite Memory Capacity$};

@@

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
             -- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
             -- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.5] {$1$}
             -- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
             -- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
             -- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
             -- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.5] {$9$}
             -- ([shift={(10, -0.65)}] t1.mid)node[legend,scale=0.5] {$10$}
             -- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.5] {$11$}
             -- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}                                      
              --([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};

@@

 		\node(t1) at ([shift={(0, -3)}] t1.mid) {};   
	    \node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=13cm, draw=white, fill=white](MC) {$Memory Capacity=6$};

   		\node(t1) at ([shift={(0, -0.8)}] t1.mid) {};                		
		\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b21) {$B$};

@@

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
		-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.5] {$1$}
		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
		-- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.5] {$9$}
		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}         
		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.5] {$14$}                                      
		-- ([shift={(15, -0.65)}] t1.mid)node[legend,scale=0.5]{$15$}
	  	-- ([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};

@@

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
		-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.5] {$1$}
		-- ([shift={(3, -0.65)}] t1.mid)node[legend,scale=0.5] {$3$}
		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
		-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.5] {$6$}         
		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}                                      
		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5]{$12$} 
		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.5] {$16$}
		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};

@@

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.5] {$5$}
		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
		-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.5] {$11$}
		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.5] {$13$}         
		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.5] {$14$} 
		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};

@@

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
		-- ([shift={(2, -0.65)}] t1.mid)node[legend,scale=0.5] {$2$}
		-- ([shift={(3, -0.65)}] t1.mid)node[legend,scale=0.5] {$3$}
		-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.5] {$6$}
		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}         
		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.5] {$16$} 
		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};

@@

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.5] {$0$}
		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.5] {$4$}
		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.5] {$8$}
		-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.5] {$11$}
		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.5] {$12$}
		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.5] {$13$}         
		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.5] {$14$}
		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.5] {$16$} 
		-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.5] {$17$}  
		--([shift={(17.1, -0.65)}] t1.mid)node[right,scale=0.5] {$t$};

@@

%%		\node[above left=0.15cm and 0cm of t2.south west, scale=0.5, rotate=0] {$GPU$};
%%		\node[above left=0.15cm and 0cm of t3.south west, scale=0.5, rotate=0] {$CPU$};		
%%		
%%		\tikzstyle{legend}=[below=0.35, anchor=mid] 	
%%		\draw[->] (-0.1, -0.1) -- (0, -0.1)  node[legend,scale=0.5] {$0$} --(1,-0.1) node [legend,scale=0.5] {$1$} --(1.5, -0.1) node[right,scale=0.5] {$t$}; 
%%		
%%		\foreach \x in {0cm, 1cm} \draw (\x, -0.12) -- (\x, -0.08);
%%		%%			To align both figures of subfloat-- an object without drawing at the same depth
%%		\path (-0.1, -0.5) -- (1.5, -0.5);

		\end{tikzpicture}
%%	} %\hspace{0.01\textwidth} %\hfill% or \hspace{5mm} or \hspace{0.3\textwidth}
%%	\subfloat[HP schedule]{
%%		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=1.8, every node/.style={scale=1.8}]
%%		\node(t1) at (0,0) {};      		
%%		
%%		\node[above right=0cm and 0cm of t1.mid, draw, minimum height=0.5cm, minimum width=0.618cm,draw,fill=white](t2) {$Y$};
%%		
%%		\node[above right=0.5cm and 0cm of t2.north west, draw, minimum height=0.5cm, minimum width=1.618cm,draw,fill=white](t3) {$X$};								
%%		
%%		\tikzstyle{legend}=[below=0.35, anchor=mid] 	
%%		\draw[->] (-0.1, -0.1) -- (0, -0.1)  node[legend,scale=0.5] {$0$} --(0.618,-0.1) node [legend,scale=0.5] {$\tfrac{1}{\phi}$} --(1.618,-0.1) node [legend,scale=0.5] {$\phi$} --(2, -0.1) node[right,scale=0.5] {$t$}; 
%%		
%%		\foreach \x in {0cm, 0.618cm, 1.618cm} \draw (\x, -0.12) -- (\x, -0.08);
%%		%%			To align both figures of subfloat -- an object without drawing at the same depth
%%		
%%		\path (-0.1, -0.5) -- (2, -0.5);
%%		
%%		\end{tikzpicture}
%%	} 
	\caption{ \label{fig:staticSchedules} Static.}
\end{figure}

>>>>

\end{itemize}
\todo[inline]{SKumar: equivalent tikz figure}
\begin{tabular}{|l|l|l|}
\hline
Task & Comm Time & Comp Time\\ \hline
A & 3 & 2\\ \hline
B & 1 & 3\\ \hline
C & 4 & 4\\ \hline
D & 2 & 1\\ \hline
\end{tabular}
	\begin{figure}[htb]
	\centering
%% 	\subfloat[Optimal schedule]{
		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=0.5, every node/.style={scale=0.5}]
		\tikzstyle{legend}=[below=0.1, anchor=mid] 	
		\node(t1) at (0,0) {};

	    \node[above right=0.4cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Infinite Memory Capacity$};

@@

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
             -- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
             -- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
             -- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
             -- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
             -- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
             -- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.65]{$9$}
             -- ([shift={(10, -0.65)}] t1.mid)node[legend,scale=0.65]{$10$}
             -- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}
             -- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}                                      
              --([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

@@

 		\node(t1) at ([shift={(0, -3.8)}] t1.mid) {};   
%%	    \node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](MC) {$Memory Capacity=6$}; 
	    \node[above right=0.4cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=9cm, draw=white, fill=white, scale=1.5](IMC) {$Memory Capacity=6$};

%%   		\node(t1) at ([shift={(0, -1.0)}] t1.mid) {};                		
		\node[above right=0cm and 0cm of t1.mid, minimum height=0.5cm, minimum width=1cm,draw,fill=white](b21) {$B$};

@@

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
		-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
		-- ([shift={(9, -0.65)}] t1.mid)node[legend,scale=0.65]{$9$}
		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}         
		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$}                                      
		-- ([shift={(15, -0.65)}] t1.mid)node[legend,scale=0.65]{$15$}
	  	-- ([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

@@

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
		-- ([shift={(1, -0.65)}] t1.mid)node[legend,scale=0.65]{$1$}
		-- ([shift={(3, -0.65)}] t1.mid)node[legend,scale=0.65]{$3$}
		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
		-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.65]{$6$}         
		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}                                      
		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$} 
		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$}
		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

@@

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
		-- ([shift={(5, -0.65)}] t1.mid)node[legend,scale=0.65]{$5$}
		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
		-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}
		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}         
		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$} 
		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

@@

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
		-- ([shift={(2, -0.65)}] t1.mid)node[legend,scale=0.65]{$2$}
		-- ([shift={(3, -0.65)}] t1.mid)node[legend,scale=0.65]{$3$}
		-- ([shift={(6, -0.65)}] t1.mid)node[legend,scale=0.65]{$6$}
		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}         
		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$} 
		--([shift={(17, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

@@

		\draw[->] ([shift={(-0.1, -0.65)}] t1.mid)
		-- ([shift={(0, -0.65)}] t1.mid)node[legend,scale=0.65]{$0$}
		-- ([shift={(4, -0.65)}] t1.mid)node[legend,scale=0.65]{$4$}
		-- ([shift={(8, -0.65)}] t1.mid)node[legend,scale=0.65]{$8$}
		-- ([shift={(11, -0.65)}] t1.mid)node[legend,scale=0.65]{$11$}
		-- ([shift={(12, -0.65)}] t1.mid)node[legend,scale=0.65]{$12$}
		-- ([shift={(13, -0.65)}] t1.mid)node[legend,scale=0.65]{$13$}         
		-- ([shift={(14, -0.65)}] t1.mid)node[legend,scale=0.65]{$14$}
		-- ([shift={(16, -0.65)}] t1.mid)node[legend,scale=0.65]{$16$} 
		-- ([shift={(17, -0.65)}] t1.mid)node[legend,scale=0.65]{$17$}  
		--([shift={(17.1, -0.65)}] t1.mid)node[right,scale=0.65]{$t$};

@@

%%		\node[above left=0.15cm and 0cm of t2.south west, scale=0.5, rotate=0] {$GPU$};
%%		\node[above left=0.15cm and 0cm of t3.south west, scale=0.5, rotate=0] {$CPU$};		
%%		
%%		\tikzstyle{legend}=[below=0.35, anchor=mid] 	
%%		\draw[->] (-0.1, -0.1) -- (0, -0.1)  node[legend,scale=0.65]{$0$} --(1,-0.1) node [legend,scale=0.65]{$1$} --(1.5, -0.1) node[right,scale=0.65]{$t$}; 
%%		
%%		\foreach \x in {0cm, 1cm} \draw (\x, -0.12) -- (\x, -0.08);
%%		%%			To align both figures of subfloat-- an object without drawing at the same depth
%%		\path (-0.1, -0.5) -- (1.5, -0.5);

		\end{tikzpicture}
%%	} %\hspace{0.01\textwidth} %\hfill% or \hspace{5mm} or \hspace{0.3\textwidth}
%%	\subfloat[HP schedule]{
%%		\begin{tikzpicture}[decoration={brace, amplitude=5},scale=1.8, every node/.style={scale=1.8}]
%%		\node(t1) at (0,0) {};      		
%%		
%%		\node[above right=0cm and 0cm of t1.mid, draw, minimum height=0.5cm, minimum width=0.618cm,draw,fill=white](t2) {$Y$};
%%		
%%		\node[above right=0.5cm and 0cm of t2.north west, draw, minimum height=0.5cm, minimum width=1.618cm,draw,fill=white](t3) {$X$};								
%%		
%%		\tikzstyle{legend}=[below=0.35, anchor=mid] 	
%%		\draw[->] (-0.1, -0.1) -- (0, -0.1)  node[legend,scale=0.65]{$0$} --(0.618,-0.1) node [legend,scale=0.65]{$\tfrac{1}{\phi}$} --(1.618,-0.1) node [legend,scale=0.65]{$\phi$} --(2, -0.1) node[right,scale=0.65]{$t$}; 
%%		
%%		\foreach \x in {0cm, 0.618cm, 1.618cm} \draw (\x, -0.12) -- (\x, -0.08);
%%		%%			To align both figures of subfloat -- an object without drawing at the same depth
%%		
%%		\path (-0.1, -0.5) -- (2, -0.5);
%%		
%%		\end{tikzpicture}
%%	} 
	\caption{ \label{fig:staticSchedules} Static.}
\end{figure}
